\documentclass[twoside,11pt]{article}

%%%%% PACKAGES %%%%%%
\usepackage{pgm2016}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{subcaption}
\usepackage[utf8]{inputenc}		
\usepackage[english]{babel}		
\usepackage{paralist}			
\usepackage[lowtilde]{url}
\usepackage{fixltx2e}
% Code formatting
\usepackage{listings}
\usepackage{color}
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}
\lstset{style=mystyle}

%%%%% MACROS %%%%%%
\algrenewcommand\Return{\State \algorithmicreturn{} }
\algnewcommand{\LineComment}[1]{\State \(\triangleright\) #1}
\renewcommand{\thesubfigure}{\roman{subfigure}}

%%%%% HEADING %%%%%%
% Heading arguments are {volume}{year}{pages}{submitted}{published}{author-full-names}
%\pgmheading{1}{2000}{1-48}{4/00}{10/00}{Cory J. Butz, Jhonatan S. Oliveira, André E. dos Santos, and Anders L. Madsen}


%%%%% SHORT HEADING %%%%%%
% Short headings should be running head and authors last names

%% My commands
\newcommand{\thistitle}{{Getting Started with Meteor}}

\ShortHeadings{\thistitle}{Oliveira}
\firstpageno{1}

\begin{document}

\title{\thistitle}

\author{\name Jhonatan S. Oliveira \email oliveira@cs.uregina.ca \\
\addr Department of Computer Science \\
University of Regina \\ 
Regina, Canada
}

\editor{CS807 - Advanced Architecture - Dr. Gerhard}

\maketitle

\begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
Meteor is considered a full-stack javascript framework.
That is, it handles from the server and data modeling to the client and user interface.
Besides this all, Meteor uses only javascript as its programming language, meaning that a whole application may be build using only javascript.
Moreover, the framework incorporate reactive programming features.
Here, the flow of the data is more focused.
In Meteor, this is tracked by using events.
A general application using the framework will keep track of events and modify database and user interface accordingly.
In this paper, we also show how Meteor can be used in resource constrains computing applications to distribute computing tasks in servers and letting the client with lightweight tasks.
\end{abstract}

\begin{keywords}
Meteor, javascript, resource constrains
\end{keywords}

% Sections
\input{sections/introduction}
\input{sections/background}
\input{sections/new_work}
\input{sections/advantages}
\input{sections/conclusions}

\vskip 0.2in
\bibliography{references/references}
\end{document}
